### 2021-04-26 submission/manuscript.Rmd
Update filenames

#Genera that were different between treatment days
#Genera that were changed by treatment
pt_d1 <- read_tsv(here("data/process/1_Day_PEG_genus_stats_PTtoD1.tsv")) %>%
  filter(p.value.adj < 0.05)
#Genera that were still different at 7 days post-infection  
pt_d7 <- read_tsv(here("data/process/1_Day_PEG_genus_stats_PTtoD7.tsv")) %>%
  filter(p.value.adj < 0.05)
pt_d7_genera <- pt_d7 %>% pull(genus)

>>>>

#Genera that were different between treatment days
#Genera that were changed by treatment
pt_d1 <- read_tsv(here("data/process/1_Day_PEG_genus_stats_BtoD1.tsv")) %>%
  filter(p.value.adj < 0.05)
#Genera that were still different at 7 days post-infection  
pt_d7 <- read_tsv(here("data/process/1_Day_PEG_genus_stats_BtoD7.tsv")) %>%
  filter(p.value.adj < 0.05)
pt_d7_genera <- pt_d7 %>% pull(genus)
